The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-03-29 paper/paper.tex
discussa mistake earlier

@@

The challenge was open to any entrants, not just those already involved in DESC, but it was
advertised primarily through Rubin, and so is perhaps best described as semi-public.
Participants developed and tested their methods locally but submitted code to be run as part of a central
combined analysis at the National Energy Research
Supercomputing Center (NERSC), where the final tests and metric evaluation were conducted.  No prize was offered apart from recognition.

@@

\subsection{Splitting nominal bin choice from assignment}
There were two ways to obtain good scores in the challenge: either one could choose the best
nominal bin edges, or find the best method to put galaxies into those bins once they are chosen.
These two are not completely disconnected: some theoretically powerful choices of nominal edges
could prove impossible to assign in practice.  But it would still have been useful to separate
the challenge into two separate parts, fixing the edges while optimizing classifiers, and vice
versa.   We can retrospectively determine this since we understand the classifiers, but the picture
would have been clearer doing so in advance.

>>>>

This meant there were two ways to obtain higher scores: either to improve the choice of nominal bin
edges, or to find better ways to assign objects to those edges.  This was a sub-optimal design decision:
separating the two issues would have enabled us to more easily delineate the advantages of different methods. 
This can be explored retrospectively, since we know what approach methods took, but would have been
easier in advance.  This and other mistakes in designing the challenge are described in \autoref{sec:mistakes}.

@@

The challenge was open to any entrants, not just those already involved in DESC, but it was
advertised through Rubin, and so is perhaps best described as semi-public.
Participants developed and tested their methods locally but submitted code to be run as part of a central
combined analysis at the National Energy Research
Supercomputing Center (NERSC), where the final tests and metric evaluation were conducted.  No prize was offered apart from recognition.

@@

\subsection{Splitting nominal bin choice from assignment}
As noted in the main test, there were two ways to obtain good scores in the challenge: 
either a team could choose the best
nominal bin edges, or find the best method to put galaxies into those bins once they are chosen.
These two are not completely disconnected: some theoretically powerful choices of nominal edges
could prove impossible to assign in practice.  But it would still have been useful to separate
the challenge into two separate parts, fixing the edges while optimizing classifiers, and vice
versa.   We can retrospectively determine this since we understand the classifiers, but the picture
would have been clearer doing so in advance.
